A longitudinal analysis of the social information in infants' naturalistic

### 2022-01-07 paper/manuscript/manuscript_dec2021_apa_blinded.Rmd
reorder appendix, integrate several google doc changes

---
title             : "A longitudinal analysis of the social information in infants' naturalistic visual experience using automated detections"
shorttitle        : "Longitudinal analysis of social information"

author: 
  - name          : "Blinded"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : ""
    email         : " "
  - name          : " "
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Blinded"

authornote: |
  The data and code that support the findings of this study are available at https://osf.io/cdhw4/.

abstract: |
    The faces and hands of caregivers and other social partners offer a rich source of social and causal information that is likely critical for infants' cognitive and linguistic development. Previous work using manual annotation strategies and cross-sectional data has found systematic changes in the proportion of faces and hands in the egocentric perspective of young infants. Here, we examine the prevalence of faces and hands in a longitudinal collection of more than 1700 headcam videos from three children ages 6 to 32 months. To analyze these naturalistic infant egocentric videos, we validated the use of a modern convolutional neural network (OpenPose) for the detection of faces and hands and then applied this model to the entire dataset. First, we found a higher proportion of hands in view than previously reported and a moderate decrease in the proportion of faces in children's view across age. Second, we found substantial variability in the proportion of faces and hands viewed by different children in different locations (e.g., living room vs. kitchen), suggesting that individual activity contexts may shape the social information that infants experience. Third, we found evidence that children may see closer, larger views of people, hands, and faces earlier in development. These analyses provide new insight into the changes in the social information in view across the first few years of life and call for further work that examines their generalizability across populations and their relationship to learning outcomes.

keywords          : "social cognition; face perception; infancy; head cameras; deep learning"
wordcount         : "X"

bibliography      : ["library.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_docx:
    includes:
      after_body: "appendix.tex"
---

@@

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=T, 
                      message=F, sanitize = T)
```

@@

Yet until recently most hypotheses about infants' visual experience have gone untested. 
Though parents and scientists alike have strong intuitions about what infants see, even the viewpoint of a walking child is hard to intuit [@clerkin2017; @franchak2011]. 
By equipping infants and toddlers with head-mounted cameras, researchers have begun to document the infant's egocentric perspective on the world [@smith2015contributions; @smith2018developing; @franchak2011] and the consequences of this changing view for early learning.
Using these methods, a growing body of work now demonstrates that the viewpoints of very young infants (less than 4 months of age) are indeed dominated by frequent, persistent views of the faces of their caregivers [@Jayaraman2015; @jayaraman2013visual; @jayaraman2017faces; @Sugden2014; @Jayaraman2018].

@@

Here, we examine the social information present in the infant visual perspective---the presence of faces and hands---by analyzing a longitudinal collection of more than 1700 headcam videos collected at home from three children along a span of 6 to 32 months of age—--the SAYCam dataset [@SAYcam]. We analyze the video data from this dense, longitudinal dataset as case studies of how the social information in the infant view changes over the course of development in individual children. These kinds of longitudinal case studies provide an important counterpoint to cross-sectional investigations for several reasons. By repeatedly recording data from the same child, they allow us to investigate developmental changes within each child and to relate these to developmental milestones (e.g., the onset of walking). Second, they eliminate several nuance sources of variability (e.g., parent/child familiarity with camera, home environment) that may obscure fine-grained developmental patterns.

Finally, longitudinal case studies allow us to investigate the ecological validity of results in everyday, naturalistic learning contexts. Indeed, in addition to its size and longitudinal nature, the SAYCam dataset is more naturalistic than those previously used in two key ways. First, recordings were taken under a large variety of activity contexts [@roy2015predicting; @bruner1985role] encompassing infants' viewpoints during both activities outside and inside the home. Even in other naturalistic datasets, the incredible variety in a typical infant's experience has been largely underrepresented (see examples in Figure 1; e.g., riding in the car, gardening, watching chickens during a walk, browsing magazines, nursing, brushing teeth). Second, the head-mounted cameras used in the SAYCam dataset captured a larger field of view than those typically used, allowing a more complete picture of the infant perspective. While head-mounted cameras with a more restricted field of view do represent where infants are foveating most of the time [@yoshida2008; @smith2015contributions], they may fail when faces or hands appear in children's peripheral vision but are still part of a joint interaction.

However, it is important to note that these data -- albeit naturalistic and densely sampled within individuals -- come from only a few children in western contexts [@@henrich2010most], and as such cannot on their own yield generalizable conclusions about developmental changes in the infant view. Instead, they serve as a testbed for validating prior developmental findings within the daily lives of individual children -- and for generating novel hypotheses that can be tested in cross-sectional datasets or targeted in-lab experiments.

With hundreds of hours of footage (>42M frames), however, this large dataset necessitates a shift to an automated annotation strategy.
Indeed, annotation of the frames extracted from egocentric videos has been prohibitively time-consuming, meaning that most frames are typically not inspected, even in the most comprehensive studies. 
For example, @Fausey2016 collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand-annotated (by four coders), totalling 103,383 frames (per coder)--an impressive number of annotations but nonetheless only 0.67% of the collected footage.

@@

We next inspected frames where OpenPose failed to detect faces/hands or erroneously detected them to gain insight into the factors driving performance. Appendix Figure \ref{fig:error_examples} shows randomly sampled examples of both missed detections and false alarms for both faces and hands and highlights the challenging detection conditions presented by these at-home, naturalistic videos. Many missed faces included very far away or very close up views of faces at odd angles, as well as faces that were partially occluded by odd lighting conditions. False alarms for faces included animal faces depicted in picture books and poses where the person was not facing a camera. Hands were sometimes erroneously detected when a pose was present but the hands were out of view, and hands were often missed when they were seen only from the side and unconnected to a pose or belonged to the child.

### Detecting children's own hands 
We thus suspected that OpenPose's low recall for hands in this dataset was because children’s own hands were often in view of the camera and unconnected to a pose -- a notoriously challenging detection problem [@bambach2015lending]. To assess this possibility, we obtained additional human annotations for the subsample of 9051 frames in the gold set frames where a hand was present; participants (recruited via Amazon Mechanical Turk) were asked to draw bounding boxes around children’s and adult’s hands. Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100`% of missed hand detections were of child hands; OpenPose was only able to detect children's hands when there were in view `r round(mean(gold_sample_child_hands$hand_detected),2)*100`% of the time. Accordingly, when frames with children's hands were removed from the gold set, recall did improve somewhat to `r round(hand_performance_adults[3],2)`. We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Appendix Figure \ref{fig:handLocation}.

### Restricting detections to the center field-of-view
Given that the fish-eye lens may have distorted the edges of the visual field in the videos, we also examined whether we would see improved precision by restricting the included detections to the center field-of-view, and excluding detections that occured in the outer 20\% of each frame. This restricted field-of-view is also more comparable to video data from other head-mounted cameras. However, we found that excluding these detections did not improve the model's precision for either faces or hands; rather, it only decreased recall. Excluding peripehral detections led to an overall f-score of `r round(face_performance_center[3],2)`, for faces with a precision of `r round(face_performance_center[1],2)` and recall of `r round(face_performance_center[2],2)`. For hands, the F-score for center detections was `r round(hand_performance_center[3],2)`, with a precision of `r round(hand_performance_center[1],2)` and recall of `r round(hand_performance_center[2],2)`. Thus, detections that were made in the periphery of these videos were not more likely to be false alarms for either faces or hands. Appendix Figure \ref{fig: density-op-fps} illustrates this finding, showing the density of false positives for both faces and hands that are concentrated in the center of the fied of view.

### Detector confidence
We next examined the degree to which including detections that the model was more or less confident in changed overall model performance for face/hand detection. When we restricted detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`. Further analyses sweeping across the entire range of possible confidence detection thresholds revealed that including all detections was the most beneficial for optimizing the rate of true positives (see Appendix Figure \ref{fig:roc_curves} for full ROC curves for both face and hand detections).

### Accuracy across child, location, and age
Finally, we examined whether model accuracy for hands and faces varied across age or between child and the location in which the videos were filmed (e.g., kitchen vs. living room). Some of the videos at taken at older ages for child A did seem to show lower hand detection accuracy, perhaps due the presence of child's hands; however, there were also fewer videos at these time points (see plots for age/child in Appendix, Figure \ref{fig:det_perf_by_age}). We did not find any discernible trends in face/hand detection accuracy across different filming locations (see Figure \ref{fig:det_perf_by_locations}). However, we did still see considerable variation in model accuracy across different videos, suggesting that particular recording activities, lighting conditions, or situations could cause conditions that would impair detector performance.

@@

However, the most striking result from these analyses is a much greater overall proportion of hands in view than has previously been reported [@Fausey2016]. We found this observation to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset, see dotted lines in Appendix Figure \ref{fig:goldSetSanity}) or OpenPose annotations on the entire dataset (see Figure \ref{fig:faceHandDetailed}A). This finding is notable especially given that OpenPose showed relatively low recall for hands, indicating that our measurements may in fact be an underestimate of the proportion of hands in view. In fact, analysis of the human gold standard annotations revealed a much higher proportion of hands relative to faces than the automated annotations.

@@

As we found that children's hands tended to occur in the lower visual field (see Figure \ref{fig:handLocation}), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, and decreasing face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%. This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure Appendix \ref{fig:handLocation}), especially as OpenPose was biased to miss children's hands when they were in view. Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:faceHandDetailed}). We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure \ref{fig:goldSetSanity}).

Finally, we analyzed how these two sources of social information co-occurred.
To do so, wecalculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range. Faces and hands were jointly present in `r sum(all_vid_data$faces_and_hands,na.rm=TRUE)/sum(all_vid_data$num_frames)*100` percent of frames (see face hand-occurrences across age in Figure \ref{fig:faceHandDetailed}C). As shown in Figure \ref{fig:faceHandContingency}, all three infants were more likely to see hands independently -- without the presence of a face -- than they were likely to see faces independently. That is, generally speaking when a face was present, a hand also tended to be present.

@@

We then used a discontinuity analysis to estimate whether the onset of each of these three motor milestones changed the proportion of faces/hands in each chid's view. Specifically, we used mixed-effects regressions with per-child random intercepts to estimate whether children's age (in months), each motor milestone, and their interaction significantly influenced the proportion of hands or faces that each child saw; see Appendix for tables with full model specifications and tables with all coefficients. Overall, we found that the age at which these children began sitting did not significantly predict changes in either the amount of faces or hands that they saw. However, as children became able to cruise, they saw significantly more faces ($\beta = 0.27$) and hands ($\beta = 0.26$), suggesting that the ability to be upright and locomote even somewhat independently was sufficient to significantly change children's visual social environment. For faces, however, there was also a significant negative interaction of age and cruising ($\beta = -0.03$, $p=0.025$), and a marginal positive effect of age ($\beta = 0.03$, $p=0.055$). However, we did not find major differences with the onset of walking; as these children became able to walk, they saw marginally more hands ($\beta = 0.09$, $p=0.052$). Thus, these analyses confirm and extend cross-sectional findings, leveraging dense, within-child data to help elucidate the complex relationship between motor development and the social information in view.

@@

How does the child's context influence the social information in view? 
@bruner1985role discussed the role of children's activities in shaping the information present for learning. Following this idea, we investigated whether there were differences in access to faces and hands by the activity that the child was engaged in. This hypothesis seems intuitively appealing. Some activities seem likely to be characterized by a much higher proportion of faces (e.g., diaper changes) than others (e.g., a car trip). Following this same idea, perhaps other activities involve the presence of more hands in the field of view (e.g., playtime). 
We did not have access to detailed annotations of activity; each video was associated with several different activities. 
Thus, following @roy2015predicting, we used spatial location as a proxy for activity context, taking advantage of the presence of these annotations for a subset of the SAYCam videos. 
In our viewing of the SAYCam videos and in other annotations available with the dataset, activities varied somewhat predictably by location: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room. However, every location was associated with multiple activities; see Appendix Figure \ref{fig:activities_by_loc} for a heatmap relating individual activities to locations in the dataset.
Of the `r num_videos` videos in the dataset, `r num_videos_annotated` were annotated for the location or locations they were filmed in. 
These location annotations were only available for two children, S and A.
Annotated locations mostly consisted of rooms of the house (e.g., "living room") but also included some other locations (e.g., "car," "outside").
Of this set, `r videos_included` videos were filmed in only a single location (e.g., the location label did not change within the video), representing 17 percent of the dataset and over 5 million frames.

@@

Finally, we also examined whether there were changes in where faces tended to appear in the camera's (and hence, by proxy, the child's) field of view. 
As expected, faces tended to be located towards the upper field of view, while views of hands were more centrally distributed (see Appendix, Figure \ref{fig:faceHandDensity} for average density distributions). 
However, we also found evidence that older children tended to see more faces in more variable positions than younger children. 
Specifically, we examined how variable the horizontal and vertical coordinates were of the faces in the infant view. 
To do so, we calculated the coefficient of variation of the horizontal (x) and vertical (y) positions of centers of the faces detected by OpenPose (see Figure \ref{fig:faceDetailed}B), and examined changes across age. 
Faces tended to be more variable in the vertical than their horizontal position (see Figure \ref{fig:faceDetailed}B). 
We also found that as children got older, they tended to see faces that varied more in their horizontal -- but not their vertical position -- suggesting that older children might be more likely to see more smaller faces in their periphery (see Figure \ref{fig:faceDetailed}B).

@@

```{r appendix, include = FALSE}
render_appendix("appendix.Rmd")
```

>>>>

---
title: A longitudinal analysis of the social information in infants' naturalistic
  visual experience using automated detections
author:
- name: Blinded
  affiliation: '1'
  corresponding: yes
  address: ''
  email: ' '
- name: ' '
  affiliation: '1'
shorttitle: Longitudinal analysis of social information
output: papaja::apa6_docx
authornote: "The data and code that support the findings of this study are available
  at https://osf.io/cdhw4/. \n"
abstract: |
  The faces and hands of caregivers and other social partners offer a rich source of social and causal information that is likely critical for infants' cognitive and linguistic development. Previous work using manual annotation strategies and cross-sectional data has found systematic changes in the proportion of faces and hands in the egocentric perspective of young infants. Here, we examine the prevalence of faces and hands in a longitudinal collection of more than 1700 headcam videos from three children ages 6 to 32 months. To analyze these naturalistic infant egocentric videos, we validated the use of a modern convolutional neural network (OpenPose) for the detection of faces and hands and then applied this model to the entire dataset. First, we found a higher proportion of hands in view than previously reported and a moderate decrease in the proportion of faces in children's view across age. Second, we found substantial variability in the proportion of faces and hands viewed by different children in different locations (e.g., living room vs. kitchen), suggesting that individual activity contexts may shape the social information that infants experience. Third, we found evidence that children may see closer, larger views of people, hands, and faces earlier in development. These analyses provide new insight into the changes in the social information in view across the first few years of life and call for further work that examines their generalizability across populations and their relationship to learning outcomes.
keywords: social cognition; face perception; infancy; head cameras; deep learning
wordcount: X
bibliography: library.bib
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: no
mask: no
draft: no
documentclass: apa6
classoption: man
affiliation:
- id: '1'
  institution: Blinded

---

@@

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)
```

@@

Yet until recently most hypotheses about infants' visual experience have gone untested. 
Though parents and scientists alike have strong intuitions about what infants see, even the viewpoint of a walking child is hard to intuit [@clerkin2017; @franchak2011].
By equipping infants and toddlers with head-mounted cameras, researchers have begun to document the infant's egocentric perspective on the world [@smith2015contributions; @smith2018developing; @franchak2011] and the consequences of this changing view for early learning.
Using these methods, a growing body of work now demonstrates that the viewpoints of very young infants (less than 4 months of age) are indeed dominated by frequent, persistent views of the faces of their caregivers [@Jayaraman2015; @jayaraman2013visual; @jayaraman2017faces; @sugden2014spy; @Jayaraman2018].

@@

Here, we examine the social information present in the infant visual perspective---the presence of faces and hands---by analyzing a longitudinal collection of more than 1700 headcam videos collected at home from three children along a span of 6 to 32 months of age—--the SAYCam dataset [@SAYcam]. We analyze the video data from this dense, longitudinal dataset as case studies of how the social information in the infant view changes over the course of development in individual children. These kinds of longitudinal case studies provide an important counterpoint to cross-sectional investigations for several reasons. By repeatedly recording data from the same child, they allow us to investigate developmental changes within each child, avoiding the ecological fallacy of assuming that between-person patterns reflect within-person mechanisms [@piantadosi1988ecological]. Second, they allow us to relate developmental changes to milestones achieved by an individual child (e.g., the onset of walking). Second, they eliminate several sources of variability (e.g., parent/child familiarity with camera, home environment) that may obscure fine-grained developmental patterns.

Finally, longitudinal case studies allow us to investigate the ecological validity of results in everyday, naturalistic learning contexts. Indeed, in addition to its size and longitudinal nature, the SAYCam dataset is more naturalistic than those previously used in two key ways. First, recordings were taken under a large variety of activity contexts [@roy2015predicting; @bruner1985role] encompassing infants' viewpoints during both activities outside and inside the home. Even in other naturalistic datasets, the incredible variety in a typical infant's experience has been largely underrepresented (see examples in Figure 1; e.g., riding in the car, gardening, watching chickens during a walk, browsing magazines, nursing, brushing teeth). Second, the head-mounted camera devices used in the SAYCam dataset captured a larger field of view than those typically used, allowing a more complete picture of the infant perspective. While head-mounted cameras with a more restricted field of view do represent where infants are foveating most of the time [@yoshida2008; @smith2015contributions], they may fail when faces or hands appear in children's peripheral vision but are still part of a joint interaction.

However, the SAYCam data – while naturalistic and densely sampled within individuals – come from only a handful of children. These are a group of three children of developmental psychologists growing up in US contexts that conform to the WEIRD rubric [@henrich2010most] for numerous reasons they cannot on their own yield generalizable conclusions about developmental changes in the infant view. Instead, they serve as a testbed for validating prior developmental findings within the daily lives of individual children – and for generating novel hypotheses that can be tested in cross-sectional datasets or targeted in-lab experiments.

With hundreds of hours of footage (>42M frames), this large dataset necessitates a shift to an automated annotation strategy.
Indeed, annotation of the frames extracted from egocentric videos has been prohibitively time-consuming, meaning that most frames are typically not inspected, even in the most comprehensive studies. 
For example, @Fausey2016 collected a total of 143 hours of head-mounted camera footage (15.5 million frames), of which one frame every five seconds was hand-annotated (by four coders), totalling 103,383 frames (per coder)--an impressive number of annotations but nonetheless only 0.67% of the collected footage.

@@

We next inspected frames where OpenPose failed to detect faces/hands or erroneously detected them to gain insight into the factors driving performance. Appendix Figure A1 shows randomly sampled examples of both missed detections and false alarms for both faces and hands and highlights the challenging detection conditions presented by these at-home, naturalistic videos. Many missed faces included very far away or very close up views of faces at odd angles, as well as faces that were partially occluded by odd lighting conditions. False alarms for faces included animal faces depicted in picture books and poses where the person was not facing a camera. Hands were sometimes erroneously detected when a pose was present but the hands were out of view, and hands were often missed when they were seen only from the side and unconnected to a pose or belonged to the child. One conclusion of this examination is that egocentric videos using cameras with larger view angles, higher resolution, and more lighting-invariant sensors may lead to better performance, even in the absence of better detection models.

### Detecting children's own hands 
We thus suspected that OpenPose's low recall for hands in this dataset was because children’s own hands were often in view of the camera and unconnected to a pose -- a notoriously challenging detection problem [@bambach2015lending]. To assess this possibility, we obtained additional human annotations for the subsample of 9051 frames in the gold set frames where a hand was present; participants (recruited via Amazon Mechanical Turk) were asked to draw bounding boxes around children’s and adult’s hands. Overall, we found that `r round(mean(hands_missed$child_hand_seg),2)*100`% of missed hand detections were of child hands; OpenPose was only able to detect children's hands when there were in view `r round(mean(gold_sample_child_hands$hand_detected),2)*100`% of the time. Accordingly, when frames with children's hands were removed from the gold set, recall did improve somewhat to `r round(hand_performance_adults[3],2)`. We also observed that children’s hands tended to appear in the lower half of the frames; heatmaps of the bounding boxes obtained from these annotations can be seen in Appendix Figure A2.

### Restricting detections to the center field-of-view
Given that the fish-eye lens may have distorted the edges of the visual field in the videos, we also examined whether we would see improved precision by restricting the included detections to the center field-of-view, and excluding detections that occured in the outer 20\% of each frame. This restricted field-of-view is also more comparable to video data from other head-mounted cameras. However, we found that excluding these detections did not improve the model's precision for either faces or hands; rather, it only decreased recall. Excluding peripehral detections led to an overall f-score of `r round(face_performance_center[3],2)`, for faces with a precision of `r round(face_performance_center[1],2)` and recall of `r round(face_performance_center[2],2)`. For hands, the F-score for center detections was `r round(hand_performance_center[3],2)`, with a precision of `r round(hand_performance_center[1],2)` and recall of `r round(hand_performance_center[2],2)`. Thus, detections that were made in the periphery of these videos were not more likely to be false alarms for either faces or hands. Appendix Figure A3 illustrates this finding, showing the density of false positives for both faces and hands that are concentrated in the center of the fied of view.

### Detector confidence
We next examined the degree to which including detections that the model was more or less confident in changed overall model performance for face/hand detection. When we restricted detections to high-confidence face/hand detections (>.5 confidence, default threshold for visualization in OpenPose) was not beneficial -- improving precision but dramatically impairing recall and thus overall performance: the F-score for high-confidence face detections was `r round(face_performance_hc[3],2)`, with a precision of `r round(face_performance_hc[1],2)` and recall of `r round(face_performance_hc[2],2)`; for high-confidence hand detections, the F-score was `r round(hand_performance_hc[3],2)`, with a precision of `r round(hand_performance_hc[1],2)` and recall of `r round(hand_performance_hc[2],2)`. Further analyses sweeping across the entire range of possible confidence detection thresholds revealed that including all detections was the most beneficial for optimizing the rate of true positives (see Appendix Figure A4 for full ROC curves for both face and hand detections).

### Accuracy across child, location, and age
Finally, we examined whether model accuracy for hands and faces varied across age or between child and the location in which the videos were filmed (e.g., kitchen vs. living room). Some of the videos at taken at older ages for child A did seem to show lower hand detection accuracy, perhaps due the presence of child's hands; however, there were also fewer videos at these time points (see plots for age/child in Appendix, Figure A5). We did not find any discernible trends in face/hand detection accuracy across different filming locations (see Figure A6). However, we did still see considerable variation in model accuracy across different videos, suggesting that particular recording activities, lighting conditions, or situations could cause conditions that would impair detector performance.

@@

However, the most striking result from these analyses is a much greater overall proportion of hands in view than has previously been reported [@Fausey2016]. We found this observation to be true across all ages, in all three children, and regardless of whether we analyzed human annotations (on the 24K random subset, see dotted lines in Appendix Figure A7) or OpenPose annotations on the entire dataset (see Figure \ref{fig:faceHandDetailed}A). This finding is notable especially given that OpenPose showed relatively low recall for hands, indicating that our measurements may in fact be an underestimate of the proportion of hands in view. In fact, analysis of the human gold standard annotations revealed a much higher proportion of hands relative to faces than the automated annotations.

@@

As we found that children's hands tended to occur in the lower visual field (see Appendix Figure A2), we thus re-analyzed the entire dataset while restricting our analysis to the center field of view, decreasing the proportion of hand detections from `r round(sum(all_vid_data$num_hands)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_hands_center,na.rm=TRUE)/sum(all_vid_data$num_frames),2)*100`%, and decreasing face detections from `r round(sum(all_vid_data$num_faces)/sum(all_vid_data$num_frames),2)*100`% to `r round(sum(all_vid_data$num_faces_center,na.rm=TRUE)/sum(all_vid_data$num_frames),3)*100`%. This cropping likely removed both the majority of detections of children's own hands but also some detections of adult hands (see Figure Appendix A2), especially as OpenPose was biased to miss children's hands when they were in view. Nonetheless, within this modified field of view, we still observed more hand detections than face detections (see dashed lines in Figure \ref{fig:faceHandDetailed}). We also still found a higher proportion of hands in view relative to faces when excluding any frames containing child hand's from the human annotated gold sample (see Appendix Figure A7).

Finally, we analyzed how these two sources of social information co-occurred.
To do so, we calculated the number of frames in which infants saw faces and hands together relative to overall proportions of faces/hands that were detected for each child and age range. Faces and hands were jointly present in `r sum(all_vid_data$faces_and_hands,na.rm=TRUE)/sum(all_vid_data$num_frames)*100` percent of frames (see face hand-occurrences across age in Figure \ref{fig:faceHandDetailed}C). As shown in Figure \ref{fig:faceHandContingency}, all three infants were more likely to see hands independently -- without the presence of a face -- than they were likely to see faces independently. That is, generally speaking when a face was present, a hand also tended to be present.

@@

We then used a discontinuity analysis to estimate whether the onset of each of these three motor milestones changed the proportion of faces/hands in each chid's view. Specifically, we used mixed-effects regressions with per-child random intercepts to estimate whether children's age (in months), each motor milestone, and their interaction significantly influenced the proportion of hands or faces that each child saw; see Appendix Tables A1-3 for full model specifications and tables with all coefficients. Overall, we found that the age at which these children began sitting did not significantly predict changes in either the amount of faces or hands that they saw. However, as children became able to cruise, they saw significantly more faces ($\beta = 0.27$) and hands ($\beta = 0.26$), suggesting that the ability to be upright and locomote even somewhat independently was sufficient to significantly change children's visual social environment. For faces, however, there was also a significant negative interaction of age and cruising ($\beta = -0.03$, $p=0.025$), and a marginal positive effect of age ($\beta = 0.03$, $p=0.055$). However, we did not find major differences with the onset of walking; as these children became able to walk, they saw marginally more hands ($\beta = 0.09$, $p=0.052$). Thus, these analyses confirm and extend cross-sectional findings, leveraging dense, within-child data to help elucidate the complex relationship between motor development and the social information in view.

@@

How does the child's context influence the social information in view? 
@bruner1985role discussed the role of children's activities in shaping the information present for learning. Following this idea, we investigated whether there were differences in access to faces and hands by the activity that the child was engaged in. This hypothesis seems intuitively appealing. Some activities seem likely to be characterized by a much higher proportion of faces (e.g., diaper changes) than others (e.g., a car trip). Following this same idea, perhaps other activities involve the presence of more hands in the field of view (e.g., playtime). 
We did not have access to detailed annotations of activity; each video was associated with several different activities. 
Thus, following @roy2015predicting, we used spatial location as a proxy for activity context, taking advantage of the presence of these annotations for a subset of the SAYCam videos. 
In our viewing of the SAYCam videos and in other annotations available with the dataset, activities varied somewhat predictably by location: for example, eating tended to occur in the kitchen, whereas playtime was the dominant activity in the living room. However, every location was associated with multiple activities; see Appendix Figure A8 for a heatmap relating individual activities to locations in the dataset.
Of the `r num_videos` videos in the dataset, `r num_videos_annotated` were annotated for the location or locations they were filmed in. 
These location annotations were only available for two children, S and A.
Annotated locations mostly consisted of rooms of the house (e.g., "living room") but also included some other locations (e.g., "car," "outside").
Of this set, `r videos_included` videos were filmed in only a single location (e.g., the location label did not change within the video), representing 17 percent of the dataset and over 5 million frames.

@@

Finally, we also examined whether there were changes in where faces tended to appear in the camera's (and hence, by proxy, the child's) field of view. 
As expected, faces tended to be located towards the upper field of view, while views of hands were more centrally distributed (see Appendix, Figure A9 for average density distributions). 
However, we also found evidence that older children tended to see more faces in more variable positions than younger children. 
Specifically, we examined how variable the horizontal and vertical coordinates were of the faces in the infant view. 
To do so, we calculated the coefficient of variation of the horizontal (x) and vertical (y) positions of centers of the faces detected by OpenPose (see Figure \ref{fig:faceDetailed}B), and examined changes across age. 
Faces tended to be more variable in the vertical than their horizontal position (see Figure \ref{fig:faceDetailed}B). 
We also found that as children got older, they tended to see faces that varied more in their horizontal -- but not their vertical position -- suggesting that older children might be more likely to see more smaller faces in their periphery (see Figure \ref{fig:faceDetailed}B).

@@
